msc dissertation

### 2021-08-11 msc dissertation code.Rmd
latest

##Try something new, see if it makes the results better
```{r, message=FALSE}
## use glm, stepwise approach to see how each factor explaining the sharing intention. The family for the model is binomial since the dependent variable is dichotomous.
glm0 <- glm(measurement ~ 1, data = pennys2r1long_nona, family = binomial(link = "logit"))

@@

summary(glm43)
summary(glm431)

#Ordinal logistic regression

install.packages("ordinal")
install.packages("ggeffects")

library(ordinal)
library(ggeffects)

ordinaldata <- pennys2r1longnodi_nona

@@

ggpredict_ordinaldata$x = factor(ggpredict_ordinaldata$x)
levels(ggpredict_ordinaldata$x) = c("False", "True")
colnames(ggpredict_ordinaldata)[c(1, 5,6)] =c("Headlineveracity", "Rating", "group")
levels(ggpredict_ordinaldata$group) = c("Control", "Treatment")
ggpredict_ordinaldata

ggplot(ggpredict_ordinaldata, aes(x = Rating, y = predicted)) + geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + theme_minimal() +facet_wrap(~group)

### reproduction of figure 2 without considering attention check

ggplot(p1, aes(x = factor(condition), y = as.numeric(percent), fill = headlineveracity)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9)) +
  xlab("Condition") + 
  ylab("Likelihood of Sharing (%)") +
  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
  scale_fill_discrete(name = "Headline Veracity", labels = c("False", "True"))

>>>>

## reproduction of figure 2 without considering attention check

ggplot(p1, aes(x = factor(condition), y = as.numeric(percent), fill = headlineveracity)) + 
  geom_bar(stat = 'identity',position = 'dodge') + 
  geom_text(
    aes(label = as.numeric (percent)), vjust = 1.5, position = position_dodge(0.9)) +
  xlab("Condition") + 
  ylab("Likelihood of Sharing (%)") +
  scale_x_discrete(labels= c("0"="Control","1"="Treatment"))+
  scale_fill_discrete(name = "Headline Veracity", labels = c("False", "True")) + labs(title = "All Subjects")

ggsave("All Subjects bar chart.png")
```

##Try something new, see if it makes the results better
###GLM
```{r, message=FALSE}
## use glm, stepwise approach to see how each factor explaining the sharing intention. The family for the model is binomial since the dependent variable is dichotomous.
glm0 <- glm(measurement ~ 1, data = pennys2r1long_nona, family = binomial(link = "logit"))

@@

summary(glm43)
summary(glm431)
```

###Ordinal logistic regression
```{r, message=FALSE}
#Ordinal logistic regression

install.packages("ordinal")
install.packages("ggeffects")
install.packages("ggrepel")

library(ordinal)
library(ggeffects)
library(ggrepel)

## All subjects
ordinaldata <- pennys2r1longnodi_nona

@@

ggpredict_ordinaldata$x = factor(ggpredict_ordinaldata$x)
levels(ggpredict_ordinaldata$x) = c("False", "True")
colnames(ggpredict_ordinaldata)[c(1,5,6)] =c("Headlineveracity", "Rating", "group")
levels(ggpredict_ordinaldata$group) = c("Control", "Treatment")
ggpredict_ordinaldata

ggplot(ggpredict_ordinaldata, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + 
  geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "All Subjects")

ggsave("All Subjects.png")

## attention check1

ordinaldata1 <- attention1nodi

str(ordinaldata1)
ordinaldata1$measurement <- as.factor(ordinaldata1$measurement)

ordinal1 <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata1, link = "logit")

summary(ordinal1)

exp(coef(ordinal1))

ggpredict_ordinal1 <- ggpredict(ordinal1, terms = c("condition","headlineveracity"))
ggpredict_ordinaldata1 = data.frame(ggpredict_ordinal1)

ggpredict_ordinal1
str(ggpredict_ordinaldata1)

ggpredict_ordinaldata1$x = factor(ggpredict_ordinaldata1$x)
levels(ggpredict_ordinaldata1$x) = c("False", "True")
colnames(ggpredict_ordinaldata1)[c(1,5,6)] =c("Headlineveracity", "Rating", "group")
levels(ggpredict_ordinaldata1$group) = c("Control", "Treatment")
ggpredict_ordinaldata1

ggplot(ggpredict_ordinaldata1, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "\u2265 1 Screener Correct")

ggsave("\u2265 1 Screener Correct.png")

##tips, \u2265 could display greater and equal to sign

## attention check2

ordinaldata2 <- attention2nodi

str(ordinaldata2)
ordinaldata2$measurement <- as.factor(ordinaldata2$measurement)

ordinal2 <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata2, link = "logit")

summary(ordinal2)

exp(coef(ordinal2))

ggpredict_ordinal2 <- ggpredict(ordinal2, terms = c("condition","headlineveracity"))
ggpredict_ordinaldata2 = data.frame(ggpredict_ordinal2)

ggpredict_ordinal2
str(ggpredict_ordinaldata2)

ggpredict_ordinaldata2$x = factor(ggpredict_ordinaldata2$x)
levels(ggpredict_ordinaldata2$x) = c("False", "True")
colnames(ggpredict_ordinaldata2)[c(1,5,6)] =c("Headlineveracity", "Rating", "group")
levels(ggpredict_ordinaldata2$group) = c("Control", "Treatment")
ggpredict_ordinaldata2

ggplot(ggpredict_ordinaldata2, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "\u2265 2 Screener Correct")

ggsave("\u2265 2 Screener Correct.png")

## attention check 3

ordinaldata3 <- attention3nodi

str(ordinaldata3)
ordinaldata3$measurement <- as.factor(ordinaldata3$measurement)

ordinal3 <- clm(measurement ~ condition + condition*headlineveracity, data = ordinaldata3, link = "logit")

summary(ordinal3)

exp(coef(ordinal3))

ggpredict_ordinal3 <- ggpredict(ordinal3, terms = c("condition","headlineveracity"))
ggpredict_ordinaldata3 = data.frame(ggpredict_ordinal3)

ggpredict_ordinal3
str(ggpredict_ordinaldata3)

ggpredict_ordinaldata3$x = factor(ggpredict_ordinaldata3$x)
levels(ggpredict_ordinaldata3$x) = c("False", "True")
colnames(ggpredict_ordinaldata3)[c(1,5,6)] =c("Headlineveracity", "Rating", "group")
levels(ggpredict_ordinaldata3$group) = c("Control", "Treatment")
ggpredict_ordinaldata3

ggplot(ggpredict_ordinaldata3, aes(x = Rating, y = predicted)) + 
  geom_point(aes(color = Headlineveracity), position =position_dodge(width = 0.5)) + geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Headlineveracity), position = position_dodge(width = 0.5), width = 0.3) + 
  theme_minimal() + facet_wrap(~group) + xlab("Likelihood of Sharing") + ylab("Predicted Probability of Sharing") + geom_label_repel(aes(label=sprintf("%.3f", predicted),fill = Headlineveracity), box.padding = 0.5, min.segment.length = unit(0, 'lines'), size = 3) + labs(title = "All 3 Screener Correct")

ggsave("All 3 Screener Correct.png")
